---
title: "What's New in tidymodels?"
author: "Max Kuhn"
---


```{r}
#| label: format-pkgs
#| results: hide

pkg <- function(x, cran = TRUE) {
  cl <- match.call()
  x <- as.character(cl$x)
  pkg_chr(x, cran = cran)
}

pkg_chr <- function(x, cran = TRUE) {
  if (cran) {
    res <- glue::glue('<span class="pkg"><a href="https://cran.r-project.org/package={x}">{x}</a></span>')
  } else {
    res <- glue::glue('<span class="pkg">{x}</span>')
  }
 res 
}
  

pkg_list <- function(x) {
  x <- unique(x)
  n <- length(x)
  x <- x[order(tolower(x))]
  x <- purrr::map_chr(x, ~ pkg_chr(.x))

  req <- cli::pluralize("You’ll need {n} package{?s} ({x}) for this chapter. 
                         You can install {?it/them} via:")
  req
}
```


## Packages to install

```{r}
#| label: installs
#| eval: false

pkgs <- paste0(
  "tidymodels/", 
  c("tune", "workflows", "important", "filtro", "tailor")
  )
pak::pak(pkgs, ask = FALSE)
```

<br> 

```{r}
#| label: setup
library(tidymodels)
library(desirability2)
library(filtro)
library(mirai) # or library(future)
library(tailor)
library(important)

tidymodels_prefer() 
```


## Some Example Data

```{r}
#| label: sim-data
set.seed(1)
sim_data <- sim_classification(num_samples = 1000, intercept = -12)

sim_data %>% count(class)

sim_split <- initial_split(sim_data, strata = class)
sim_train <- training(sim_split)
sim_rs <- vfold_cv(sim_train)
```

<br> 

There are 15 numeric predictors with various linear and nonlinear effects. 

## A Cost-Sensitive Neural Network

```{r}
#| label: mlp-cost

mlp_wt_spec <-
  mlp(hidden_units = tune(), penalty = tune(), learn_rate = tune(), 
      epochs = 500, activation = tune()) |>
  set_engine("brulee", stop_iter = 3, class_weights = tune()) |>
  set_mode("classification")

rec <- recipe(class ~ ., data = sim_train) |>
  step_normalize(all_numeric_predictors())

mlp_wt_wflow <- workflow(rec, mlp_wt_spec)

mlp_wt_param <- 
  mlp_wt_wflow %>% 
  extract_parameter_set_dials() %>% 
  update(
    class_weights = class_weights(c(1, 50)),
    penalty = penalty(c(-10, -1))
    )
```

## Basic Grid Search

```{r}
#| label: mlp-wt-code
#| eval: false

cls_mtr <- 
  metric_set(brier_class, roc_auc, kap, sensitivity, specificity, mn_log_loss)

mlp_wt_res <- 
  mlp_wt_wflow |>
  tune_grid(
    resamples = sim_rs,
    grid = 25,
    control = control_grid(save_pred = TRUE),
    metrics = cls_mtr,
    param_info = mlp_wt_param
  )
```

## Parallel Processing Updates

tidymodels has always used the `r pkg(foreach)` package to enable parallel processing. Sadly, we've decided to move to packages that are being actively developed. 

<br> 

The `r pkg(tune)` 2.0 disables `r pkg(foreach)` and enables the use of either the `r pkg(future)` or `r pkg(mirai)` packages: 

:::: {.columns}

::: {.column width="38%"}
`r pkg(foreach)` (deprecated):

```{r}
#| label: foreach-code
#| eval: false
#| code-line-numbers: false

library(doParallel)
cl <- makePSOCKcluster(cores)
registerDoParallel(cl)

# your code

stopCluster(cl)
```
:::

::: {.column width="35%"}
`r pkg(future)`:

```{r}
#| label: future-code
#| eval: false
#| code-line-numbers: false

library(future)
plan("multisession", cores)

# your code
```
:::

::: {.column width="27%"}
`r pkg(mirai)`:

```{r}
#| label: mirai-code
#| eval: false
#| code-line-numbers: false

library(mirai)
daemons(cores)

# your code
```
:::

::::


## Multiparameter Optimization

```{r}
#| label: selects

select_best(mlp_wt_res, metric = "sensitivity")

select_best(mlp_wt_res, metric = "specificity")

select_best(mlp_wt_res, metric = "brier_class")
```


## Postprocessing


## Tailor


## Feature selection



## Quantile Regression


## Sparse Data


## catboost



## AI Tools


## What's Next

We'll still be working on adding quantile regression to `r pkg(tune)`, `r pkg(yardstick)`, and other packages. 

<br> 

I we have time, we might also include more causal inference tools. 

<br>

I suspect that, around the new year, we'll move into a ["Snow Leopard"](https://en.wikipedia.org/wiki/Mac_OS_X_Snow_Leopard) phase where we concentrate on cleaning up more after our latests releases, add additional documentation, and refactoring our extra testing suite (which really needs some love). 